### 2024-02-17 documentation/thesis/thesis_document.tex
.

\gls{mri} stands as a cornerstone in clinical diagnostics, utilizing the
principles of nuclear magnetic resonance \gls{nmr} to generate
cross-sectional black-and-white images of the body. This indispensable
method plays a central role in contemporary medicine and research,
contributing significantly to saving lives. Despite its widespread use,
traditional \gls{mri} systems often rely on large, heavy, and expensive
magnets to achieve the necessary homogeneity of the magnetic field for
accurate imaging. \customcite{NK16}

Various types of magnets are applicated in different \gls{mri} systems.
Permanent magnets generate a steady yet relatively weak magnetic field,
electromagnets are energized by electrical currents and superconducting
electromagnets produce magnetic fields through electric induction.
Regardless of the type, the primary objective is to create a homogeneous
magnetic field within the \gls{mri}. The higher the homogeneity, the
more accurate the measurements. Homogeneity in composed \gls{mri} can be
adapted using the shimming procedure which requires a lot of effort and
is prone to errors. This uniform magnetic field aligns the molecules
within the body or object, setting the stage for a second magnetic
system to stimulate these molecules for spin-measurements.

@@

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is taken into account. It is less cost-intensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri} system.

@@

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at different locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. The accompanying open-source software for this thesis is designed
not only to facilitate measurements with different sensors but also to
enable the characterisation of different objects.

@@

At last, the temperature drift is measured by repeating the background
noise test in different temperature environments. Sensor noise should be
less than \emph{50\(\mu\)T} to characterise precisely a magnetic field
in a Halbach-Array of an \gls{mri}with precision greater than
\emph{1000\gls{ppm}}.

@@

The positioning of permanent magnets holds an important role in
constructing an \gls{mri} and is influencing the homogeneity of the
\emph{B0} magnetic field. Halbach ring magnets \customcite{H80} have
become a common design for low field \gls{mri} and \gls{nmr} systems
\customcite{SB10}.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
  \customcite{BC16}
\end{itemize}

@@

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of 50.4mT, and an impressive
homogeneity of 2400\gls{ppm} over a \emph{20cm} diameter using smaller
magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables
the utilization of coil-based gradients for spatial encoding,
significantly enhancing the flexibility of image acquisition.

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
homogeneity enables the utilization of coil-based gradients for spatial
encoding, significantly enhancing the flexibility of image acquisition.

@@

Special algorithms from various, public projects are used to optimize
homogeneity, like a genetic algorithms which O'Reilly implemented
\customcite{O24}. Therefore, the challenge is to ensure the seamless
integration and compatibility of these algorithms into the overall
process. This should make it possible to create a workflow from the
individual magnet to the finished optimized \gls{cad} model of a Halbach
ring.

@@

The focus of the ongoing efforts is to improve the homogeneity of
magnets within low-field \gls{mri}systems below \emph{1000}\gls{ppm},
primarily driven by the goal of establishing a compact low-field
\gls{mri} for breast cancer detection.

@@

In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below 1000\gls{ppm}. While O'Reilly,
Teeuwisse, and Webb were able to modify the ring diameter to influence
field homogeneity, the unique goal at this point is to characterize the
magnets pre-installation, allowing for proactive assessments of
homogeneity characteristics. This approach aims to provide insights into
magnetic field uniformity before the magnets are integrated, thereby
streamlining the optimisation process. Furthermore,

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of
\emph{1000}\gls{ppm}. Furthermore, the study seeks to validate whether
the measuring range of these sensors appropriately corresponds to the
required field strength, ensuring their suitability for the intended
application.

@@

Before naming the research focus, it is important to understand the
difference and connection between deviation and resolution of the
system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
\emph{50mT} magnetic field, a resolution that is less than
\emph{1000}\gls{ppm} of \emph{50mT} is needed.

@@

\begin{itemize}
\item
  Sensor characterisation: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than \emph{1000}\gls{ppm}? The desired outcome
  is a measurement of less than \emph{50} \(\mu\)T at
  \emph{1000}\gls{ppm}, with a specific focus on determining the
  sensors' viability for noise measurements.
\end{itemize}

@@

The following chapter defines possible use cases that the future project
need to cover. These use cases define the setup of the hard- and
software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The use cases are defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process in chapter \ref{use-case-evaluation}, the defined use cases are
also used as a reference to demonstrate the implemented capabilities of
the solution. This is essential for understanding the needs of the
target group and designing the end result accordingly.

@@

Finally, a comprehensive hardware and software framework needs to be
established, which is capable of measuring diverse objects using various
sensors. Additionally, remarks need to be provided regarding the
suitability of the employed sensors for magnetic field measurements.

@@

It simplifies of own measuring devices into the \gls{mrp} ecosystem at a
later date. This is only applicable with a minimal functional hardware
and firmware setup; it is developed for this purpose in the first step.

@@

The selection process for possible magnetic field sensors initially
focisses on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.

@@

In the \emph{Evaluation} in chapter \ref{evaluation} basic
characterisation methods are used to evaluate the sensors listed in
table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
with regard to their sensitivity and other parameters. This is done at
this point, as the components of the readout interface that enable
interaction with the sensors are considered first.

@@

All parts are produced using 3D printing additive manufacturing proces.
The sensor circuit board is glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised.

The exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets have to be
measured, where the positioning over the sensor must always be the same.

@@

The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
Pico} and a \emph{STM32F4} are used as an computer-sensor interface for
this thesis, which are populare, cost-effective and simple to implement.

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These hole are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~temperature sensors).

Special attention is paid to the provision of an accessible
SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
synchronization and also offers options for later sensor-extensions.
This functionality opens up the possibility of synchronising data from
different sensors to achieve precise and coherent measurement results.
Overall, this integrated approach represents an effective solution for
the flexible evaluation of sensors and helps to optimise the development
process.

@@

It handles communication with sensors, actuators and other peripheral
devices, processing data and making decisions. Firmware is critical to
the functioning of devices.

@@

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
is implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware needs to be
integrated, only the required functions in listing
\ref{lst:CustomSensorClass} need to be implemented.

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support into the unified sensor firmware package}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor
{
public:
  CustomSensor();
  ~CustomSensor();
  // implement depending sensor communication interface
  bool begin(TwoWire& _wire_instance); // I2C
  bool begin(HardwareSerial& _serial_instance); // UART
  bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
  // FUNCTIONS USED BY READOUT LOGIC
  bool is_valid() override;
  String capabilities() override;
  String get_sensor_name() override;
  bool query_sensor() override;
  sensor_result get_result() override;
};
#endif
\end{lstlisting}

@@

The next initialisation system is dedicated for multi-sensor
synchronisation described in chapter
\ref{sensor-syncronisation-interface}. The last step in the setup is to
configure communication with the host or connected \gls{pc}. All
implemented microcontroller platforms used (\emph{Raspberry Pi Pico},
\emph{STM32F4}) have a \gls{usb} slave port.

@@

After execution of the setup routine is completed, the system switches
to an infinite loop, which processes several possible actions. One task
is, to react to user commands which can be sent to the system by the
user via the integrated \gls{cli}. All sensors are read out via a timer
interval set in the setup procedure and their values are stored in a
ring buffer. Ring buffer offers efficient data management in limited
memory. Its cyclic structure enables continuous overwriting of older
data, saves memory space and facilitates seamless processing of
real-time data.

@@

This ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized in time like described in chapter
\ref{sensor-syncronisation-interface} and are not out of sequence or
drift.

@@

\hypertarget{sensor-syncronisation-interface}{%
\subsection{Sensor Syncronisation
Interface}\label{sensor-syncronisation-interface}}

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to various factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise
latencies.\customcite{W19} Nevertheless, complex data processing tasks and
overloaded \gls{usb} ports can lead to delays.

@@

It can be seen that a jitter time of up to an additional \emph{1ms} is
added between the triggering of the measurements by the host system and
the receipt of the command by the sensor hardware. If the host system is
still under load, this value increases many times over. This means that
synchronising several sensors via the \gls{usb} connection alone is not
sufficient.

@@

In order to enable the most stable possible synchronisation between
several sensors, an option has already been created to establish an
electrical connection between sensors. This is used together with the
firmware to synchronise the readout intervals. The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together in
order to implement this form of synchronisation.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. The figure
\ref{Unified_sensor_fiUnified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.pngrmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
shows how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The firmware-function
\emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the funtionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

The table
\ref{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}
shows the various prototype sensor platforms equipped with different
magnetic field sensors. These cover all the required functions described
in the use cases \ref{use-cases}. The most important difference, apart
from the sensor used, is the \emph{scan mode}. In this context, this
describes whether the sensor can measure a \emph{static} fixed point on
the magnet or if the sensor can move \emph{dynamically} around the
magnet using a controllable manipulator.

@@

The electrical level is based on a \emph{Raspberry Pi Pico} together
with the \emph{MMC5603NJ} magnetic sensor. The mechanical setup consists
of four 3D printed components, which are fixed together with nylon
screws to minimise possible influences on the measurement.

@@

The designed magnet holder can be adapted for different magnet shapes
and can be placed on the spacer without backlash in order to be able to
perform a repeatable measurement without introducing measurement
irregularities by mechanically changing the magnet.

@@

The magnet sensor is mounted on a movable arm, which can move 180
degrees around the magnet on one axis. In order to be able to map the
full sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}.

@@

This software or hardware integration can be carried out on any other
measuring device with a suitable communication interface and a known
protocol thanks to the modular design.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}
\caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}}
\end{figure}

@@

As a result, there are two projects which are both suitable for the task
of optimizing and creating Halbach magnets for \gls{mri} applications.
The data structures are not compatible with each other. However, they
are executed manually one after the other to obtain a final result with
manual data conversation.

@@

The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. Idal magnets are assumed at this point. However, it
should also be possible to import field data in a more measured form
later on. Using the DataAquisition sub-step, it is possible to generate
any number of ideal magnets.

@@

Next, the user creates his own analysis step in order to be able to call
up its functions. In the case of the \emph{HalbachOptimisation}
\customcite{O24} project, the function signature of the start function
must be changed. This receives the result of the previous step, in this
case the generated magnet data. By optionally setting meta data in the
universal library data type, constants can be replaced in the analysis
function and made dynamically configurable. The return result also
corresponds to this data type so that subsequent steps are compatible
and contains the magnet data with modified position and rotation data.

@@

The last step is to call up the \emph{MWO24} \customcite{MWO24} project,
which creates the \gls{cad} model of the magnet holder. The data can
also be exported as files. To make the project compatible, the function
signatures are also adapted. In this case, more changes are required, as
the configuration file is loaded from the file system. This logic needs
to be removed in order to use the added meta data as input parameter
instead.

@@

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a simple text
editor. This eliminates all binary-based formats such as the
\href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
package.

Taking these points into account, the \gls{json} format is chosen. This
is human and machine readable and there is a compatible parser for
almost every programming language.

>>>>

\gls{mri} stands as a cornerstone in clinical diagnostics, utilizing the
principles of nuclear magnetic resonance \gls{nmr} to generate
cross-sectional black-and-white images of the body. This indispensable
method plays a significant role in contemporary medicine and research,
contributing significantly to saving lives. Despite its widespread use,
traditional \gls{mri} systems often rely on large, heavy, and expensive
magnets to achieve the necessary homogeneity of the magnetic field for
accurate imaging. \customcite{NK16}

Several types of magnets are applicated in different \gls{mri} systems.
Permanent magnets generate a steady yet relatively weak magnetic field,
electromagnets are energized by electrical currents and superconducting
electromagnets produce magnetic fields through electric induction.
Regardless of the type, the primary objective is to create a homogeneous
magnetic field within the \gls{mri}. The higher the homogeneity, the
more accurate the measurements. Homogeneity in composed \gls{mri} can be
adapted using the shimming procedure which requires a lot of effort and
is prone to errors. This uniform magnetic field aligns the molecules
within the body or object, setting the stage for a second magnetic
system to stimulate these molecules for spin-measurements.

@@

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is considered. It is less cost-intensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri} system.

@@

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at various locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. The accompanying open-source software for this thesis is designed
not only to facilitate measurements with different sensors but also to
enable the characterisation of different objects.

@@

At last, the temperature drift is measured by repeating the background
noise test in different temperature environments. Sensor noise should be
less than \emph{50\(\mu\)T} to characterise precisely a magnetic field
in a Halbach-Array of an \gls{mri} with precision greater than
\emph{1000 \gls{ppm}}.

@@

The positioning of permanent magnets holds a significant role in
constructing an \gls{mri} and is influencing the homogeneity of the
\emph{B0} magnetic field. Halbach ring magnets \customcite{H80} have
become a common design for low field \gls{mri} and \gls{nmr} systems
\customcite{SB10}.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Various materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
  \customcite{BC16}
\end{itemize}

@@

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of 50.4mT, and an impressive
homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm} diameter using
smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity
enables the utilization of coil-based gradients for spatial encoding,
significantly enhancing the flexibility of image acquisition.

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm}
diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
homogeneity enables the utilization of coil-based gradients for spatial
encoding, significantly enhancing the flexibility of image acquisition.

@@

Special algorithms from various, public projects are used to optimize
homogeneity, like a genetic algorithm which O'Reilly implemented
\customcite{O24}. Therefore, the challenge is to ensure the seamless
integration and compatibility of these algorithms into the overall
process. This should make it possible to create a workflow from the
individual magnet to the finished optimized \gls{cad} model of a Halbach
ring.

@@

The focus of the ongoing efforts is to improve the homogeneity of
magnets within low-field \gls{mri}systems below \emph{1000 \gls{ppm}},
primarily driven by the goal of establishing a compact low-field
\gls{mri} for breast cancer detection.

@@

In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below \emph{1000 \gls{ppm}}. While
O'Reilly, Teeuwisse, and Webb were able to modify the ring diameter to
influence field homogeneity, the unique goal at this point is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This approach aims to
provide insights into magnetic field uniformity before the magnets are
integrated, thereby streamlining the optimisation process. Furthermore,

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of \emph{1000
\gls{ppm}}. Furthermore, the study seeks to validate whether the
measuring range of these sensors appropriately corresponds to the
required field strength, ensuring their suitability for the intended
application.

@@

Before naming the research focus, it is important to understand the
difference and connection between deviation and resolution of the
system. To measure a deviation of better than \emph{1000 \gls{ppm}} in a
\emph{50mT} magnetic field, a resolution that is less than \emph{1000
\gls{ppm}} of \emph{50mT} is needed.

@@

\begin{itemize}
\item
  Sensor characterisation: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than \emph{1000 \gls{ppm}}? The desired
  outcome is a measurement of less than \emph{50} \(\mu\)T at \emph{1000
  \gls{ppm}}, with a specific focus on determining the sensors'
  viability for noise measurements.
\end{itemize}

@@

The following chapter defines desirable use cases that the future
project need to cover. These use cases define the setup of the hard- and
software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The use cases are defined during project planning and provide an
overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process in chapter \ref{use-case-evaluation}, the defined use cases are
also used as a reference to demonstrate the implemented capabilities of
the solution. This is essential for understanding the needs of the
target group and designing the result accordingly.

@@

Finally, a comprehensive hardware and software framework needs to be
established, which can measure diverse objects using various sensors.
Additionally, remarks need to be provided regarding the suitability of
the employed sensors for magnetic field measurements.

@@

It simplifies of own measuring devices into the \gls{mrp} ecosystem
later. This is only applicable with a minimal functional hardware and
firmware setup; it is developed for this purpose in the first step.

@@

The selection process for possible magnetic field sensors initially
focuses on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.

@@

In the \emph{Evaluation} in chapter \ref{evaluation} basic
characterisation methods are used to evaluate the sensors listed in
table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
regarding their sensitivity and other parameters. This is done at this
point, as the components of the readout interface that enable
interaction with the sensors are considered first.

@@

All parts are produced using 3D printing additive manufacturing process.
The sensor circuit board is glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised.

The exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
Pico} and a \emph{STM32F4} are used as a computer-sensor interface for
this thesis, which are popular, cost-effective and simple to implement.

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These holes are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~temperature sensors).

Special attention is paid to the provision of an accessible
SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
synchronization and offers options for later sensor-extensions. This
functionality opens the possibility of synchronising data from different
sensors to achieve precise and coherent measurement results. Overall,
this integrated approach represents an effective solution for the
flexible evaluation of sensors and helps to optimise the development
process.

@@

It manages communication with sensors, actuators and other peripheral
devices, processing data and making decisions. Firmware is critical to
the functioning of devices.

@@

A key component is that as many common sensors as possible can be easily
connected without having to adapt the firmware. This modularity is
implemented using abstract class design. These are initiated according
to the sensors found at startup. If new hardware needs to be integrated,
only the required functions in listing \ref{lst:CustomSensorClass} need
to be implemented.

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support into the unified sensor firmware package}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor
{
public:
  CustomSensor();
  ~CustomSensor();
  // implement depending on sensor communication interface
  bool begin(TwoWire& _wire_instance); // I2C
  bool begin(HardwareSerial& _serial_instance); // UART
  bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like one wire
  // FUNCTIONS USED BY READOUT LOGIC
  bool is_valid() override;
  String capabilities() override;
  String get_sensor_name() override;
  bool query_sensor() override;
  sensor_result get_result() override;
};
#endif
\end{lstlisting}

@@

The next initialisation system is dedicated for multi-sensor
synchronisation described in chapter
\ref{sensor-synchronisation-interface}. The last step in the setup is to
configure communication with the host or connected \gls{pc}. All
implemented microcontroller platforms used (\emph{Raspberry Pi Pico},
\emph{STM32F4}) have a \gls{usb} slave port.

@@

After execution of the setup routine is completed, the system switches
to an infinite loop, which processes several actions. One task is, to
react to user commands which can be sent to the system by the user via
the integrated \gls{cli}. All sensors are read out via a timer interval
set in the setup procedure and their values are stored in a ring buffer.
Ring buffer offers efficient data management in limited memory. Its
cyclic structure enables continuous overwriting of older data, saves
memory space and facilitates seamless processing of real-time data.

@@

This ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized in time like described in chapter
\ref{sensor-synchronisation-interface} and are not out of sequence or
drift.

@@

\hypertarget{sensor-synchronisation-interface}{%
\subsection{Sensor Synchronisation
Interface}\label{sensor-synchronisation-interface}}

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to numerous factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise
latencies.\customcite{W19} Nevertheless, complex data processing tasks and
overloaded \gls{usb} ports can lead to delays.

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.

@@

To enable the most stable possible synchronisation between several
sensors, an option has already been created to establish an electrical
connection between sensors. This is used together with the firmware to
synchronise the readout intervals. The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. The figure
\ref{Unified_sensor_fiUnified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.pngrmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
shows how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The firmware-function
\emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

The table
\ref{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}
shows the various prototype sensor platforms equipped with different
magnetic field sensors. These cover all the required functions described
in the use cases \ref{use-cases}. The most significant difference, apart
from the sensor used, is the \emph{scan mode}. In this context, this
describes whether the sensor can measure a \emph{static} fixed point on
the magnet or if the sensor can move \emph{dynamically} around the
magnet using a controllable manipulator.

@@

The electrical level is based on a \emph{Raspberry Pi Pico} together
with the \emph{MMC5603NJ} magnetic sensor. The mechanical setup consists
of four 3D printed components, which are fixed together with nylon
screws to minimise influences on the measurement.

@@

The designed magnet holder can be adapted for different magnet shapes
and can be placed on the spacer without backlash to be able to perform a
repeatable measurement without introducing measurement irregularities by
mechanically changing the magnet.

@@

The magnet sensor is mounted on a movable arm, which can move 180
degrees around the magnet on one axis. To be able to map the full
sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}.

@@

This software or hardware integration can be conducted on any other
measuring device with a suitable communication interface and a known
protocol thanks to the modular design.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
\caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
using a \gls{usb} to serial converter and needed additional pull-up
resistors
\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}}
\end{figure}

@@

As a result, there are two projects which are both suitable for the task
of optimizing and creating Halbach magnets for \gls{mri} applications.
The data structures are not compatible with each other. However, they
are executed manually one after the other to obtain a result with manual
data conversation.

@@

The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. Idal magnets are assumed at this point. However, it
should also be possible to import field data in a more measured form
later. Using the DataAquisition sub-step, it is possible to generate any
number of ideal magnets.

@@

Next, the user creates his own analysis step to be able to call up its
functions. In the case of the \emph{HalbachOptimisation} \customcite{O24}
project, the function signature of the start function must be changed.
This receives the result of the previous step, in this case the
generated magnet data. By optionally setting meta data in the universal
library data type, constants can be replaced in the analysis function
and made dynamically configurable. The return result also corresponds to
this data type so that subsequent steps are compatible and contains the
magnet data with modified position and rotation data.

@@

The last step is to call up the \emph{MWO24} \customcite{MWO24} project,
which creates the \gls{cad} model of the magnet holder. The data can
also be exported as files. To make the project compatible, the function
signatures are also adapted. In this case, more changes are required, as
the configuration file is loaded from the file system. This logic needs
to be removed to use the added meta data as input parameter instead.

@@

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a plain text
editor. This eliminates all binary-based formats such as the
\href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
package.

Taking these points into account, the \gls{json} format is chosen. This
is human and machine readable and there is a compatible parser for every
programming language.
